---
title: "Besemah stress"
author: "Bradley McDonnell"
date: "1/1/2019"
output: 
  ioslides_presentation:
    widescreen: true
    smaller: false
    incremental: true
    transition: slower 
always_allow_html: yes
bibliography: bib/besemah-stress.bib

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(htmltools.dir.version = FALSE)
```

```{r data, include=FALSE}

# Loading libraries
library(tidyverse)
library(knitr)
library(kableExtra)

# Loading the dataframe
pse_stress <- read_tsv("data/pse-stress-simplified.csv") %>% 
                          mutate(Word = fct_recode(Word),
                                Position = fct_recode(Position),
                                Vowel = fct_recode(Vowel),
                                Weight = fct_recode(Weight),
                                Focus = fct_recode(Focus),
                                Final = fct_recode(Final),
                                Participant = fct_recode(Participant),
                                Final = fct_relevel(Final, "non-final", "final")
                                )
                          
                        
head(pse_stress)
```

## Overview

- Present study is designed to tease apart different factors relating to prosodic prominence in Besemah. 
- Investigates realization of common acoustic correlates of stress 
  - f$_0$
  - duration
  - intensity
  - spectral tilt 
- within target words that vary 
  - in their sentence position (sentence-medial vs. sentence-final position) 
  - information status ('in focus' vs. 'out of focus').

## Introduction

1. There has been much disagreement over the status of word-level stress in the languages of western Indonesia [see @vanzanten2003status].
1. Word-level stress has been claimed to fall predictably on the penultimate syllable unless it contains a schwa in which case it falls on the ultima [@adisasmito1996phonetic]
1. An increasing number of studies have questioned this position for Standard Indonesian [@vanzanten2004word]


## Design
1. Target words were collected using an information gap task.
1. This task involved two talkers: a confederate who asked questions and a naive participant who answered them.
1. One female native speaker of Besemah acted as the confederate for all participants.

## Materials

|**Position** |       |    **Question/Answer**                    |  
|-------------|-------|-------------------------------------------|
|    final    | Q:    |  *Sebelah kanan kate ape?*                |
|             |       | 'On the right side is what word?'         |
|             | A:    | *Sebelah kanan kate **susu**.*            |
|             |       | 'On the right side is **milk**.'          |
|    medial   | Q:    | *Kate ape sebelah kanan?*                 |
|             |       | 'What word is on the right side?'         |
|             | A:    | *Kate* ***susu*** *sebelah kanan.*        |
|             |       | 'The word **milk** is on the right side.'||


## Words 

|**Phoneme**| **Word** |                |
|-----------|----------|----------------|
| /i/       | /titi/   | 'to cross over'|
|           | /pipis/  | 'to pulverize' |
|           | /tʃiŋki/ | 'must have'    |
|           | /sintiŋ/ | 'crooked'      |
| /u/       | /susu/   | 'milk'         |
|           | /tutus/  | 'to pound'     |
|           | /tuŋku/  | 'hearth'       |
|           | /tuntun/ | 'to watch'     |
| /a/       | ---      |                | 
|           | /tatap/  | 'to touch'     |
|           | ---      |                |
|           | /pantas/ | 'to be fitting'|
| /ə/       | /tʃətə/  | 'to be exact'  |
|           | ---      |                |
|           | /təmpə/  | 'to forge'     |
|           | ---      |                | 


## Procedure 

- Block A: sentence-medial, 'in focus'
- Block B: sentence-final, 'in focus'
- Block C: sentence-medial, 'out of focus'
- Block D: sentence-final, 'in focus'

## Duration

```{r duration-final}
# A simple boxplot of intensity
dur <- ggplot(pse_stress, aes(Position, Duration))
dur + geom_boxplot() + facet_wrap(~Final, ncol = 1) + coord_flip() + scale_x_discrete(limits = rev(levels(pse_stress$Position)))
```

## Duration

```{r dur-mean-fin}
pse_stress %>% 
  group_by(Position, Final) %>%
  summarize(Duration = round(mean(Duration), 3)) %>%
  kable() %>%
  kable_styling(full_width = TRUE) %>%
  collapse_rows(columns = 1, valign = "middle")
```

## Conclusion

- There are some interesting data here, but we cannot conclude much at this point. 

---- 


<!-- Note ---- is how you create a slide without a title in case you're curious -->

Go to <https://bookdown.org/yihui/rmarkdown/ioslides-presentation.html> for more ideas of what to do with your slides. 

For even more on **isoslides** go to <https://openscience.nuance-r.com/ioslides_presentation_format.html>

For `kable` tables, go to <https://haozhu233.github.io/kableExtra/awesome_table_in_html.html>

For another style of slides using R Markdown, see `xaringan` <https://github.com/yihui/xaringan>

If you are interested in bibliographies see <https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html>

----

If you want to number tables, see: 
<https://www.r-bloggers.com/r-markdown-how-to-number-and-reference-tables/>

If you wanted to look at potential article templates: 
<https://github.com/rstudio/rticles>

Some other table options in R Markdown: 
<https://davidgohel.github.io/flextable/index.html>

Tips for using knitr and R Markdown with Word (.docx) files
<https://rmarkdown.rstudio.com/articles_docx.html>


## References
